\pkg{Rgbp}: An R Package for Hierarchical Modeling and Method Checking

### 2013-06-26 jss/article.tex
changes

%% an abstract and keywords
\Abstract{Bayesian-frequentist reconciliation via Bayesian hierarchical modeling for Gaussian, Binomial, and Poisson data and frequentist method check for good coverage probability.}
\Keywords{hierarchical model, multilevel model, random effects mixed model, method check, coverage probability, normal, binomial, poisson, shrinkage, \proglang{R}}
\Plainkeywords{keywords, comma-separated, not capitalized, r} %% without formatting
%% at least one keyword must be supplied

@@

%TODO: Do we want this here? Or just go straight into theory then follow with examples?
\section[Feasible Data Types]{Three Feasible Types of Data }
\pkg{Rgbp} is intended to fit a model where two levels of structure are assumed (unit and group levels). The model can be characterized by the distributional family assumed for the group level data and in the case of \pkg{Rgbp} this will be either the Normal, Poisson, or Binomial distribution. In this section, we will introduce three specific types of feasible data sets that illustrate this fact.

\subsection{Normal: 8 Schools} \label{8schooldata}
The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (group) to test whether students (unit) SAT scores are effected by coaching. The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \cite{1981}.
\begin{CodeChunk}
\begin{CodeInput}
R> y  <- c(12, -3, 28,  7,  1,  8, 18, -1)
R> se <- c(18, 16, 15, 11, 11, 10, 10,  9)
\end{CodeInput}
\end{CodeChunk}

Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated. So, it is reasonable to think that each school-level coaching effect is distributed as an independent Normal distribution given the unknown mean $\mu_{j}$ and known standard error:  $y_{j}\vert\mu_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$. \pkg{Rgbp} includes this data set and can be called by the command `\code{data(schools)}' on \proglang{R}.

\subsection{Poisson: 31 Hospitals}
The following data are from medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 \cite{2012}. It comprises of the number of deaths within a month of CABG surgeries in each hospital ($z_{j},~j=1, \ldots, 31$) and the total number of patients receiving CABG surgeries (case load) in each hospital ($n_{j},~j=1, \ldots, 31$). The following code is an example of input based on the last ten hospital data.
\begin{CodeChunk}
\begin{CodeInput}
R> z <- c( 14,   9,  15,  13,  35,  26,  25,  20,   35,   27)
R> n <- c(593, 602, 629, 636, 729, 849, 914, 940, 1193, 1340)
\end{CodeInput}
\end{CodeChunk}
Considering the type of data, it is reasonable to assume the number of deaths in each hospital follow independent Poisson distributions given an unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where, for each $j$, $n_{j}$ can be interpreted as an exposure (not necessarily an integer) and $\lambda_{j}$ as the true death rate per exposure. This data set is also included in the package and can be called by `\code{data(hospital)}' on \proglang{R}.

\subsection{Binomial: 18 Baseball Hitters}
The following dataset contains information on the batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season \cite{1975}. In addition one covariate relating to the position each player was playing was observed and for illustrative purposes, we transform this variable into a binary indicator (1 if a player was a outfielder and 0 otherwise).
\begin{CodeChunk}
\begin{CodeInput}
R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
\end{CodeInput}
\end{CodeChunk}
The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown true batting average $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$. This data set is also a part of the package and can be called on \proglang{R} by `\code{data(baseball)}'.

\section[Multilevel Structure]{Multilevel Structure} \label{multilevel}
A two-level or multilevel model, also called a conditionally independent hierarchical model \cite{1989}, is a very powerful tool for exploring the hierarchical structure in data. For example, in the 8 schools dataset, we can imagine that there exists a district-level hierarchy (bigger population) for 8 schools, the state-level hierarchy for 31 hospitals, and the position-level hierarchy for 18 baseball players. \code{gbp}, one of the functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter. The \code{gbp} function allows users to choose one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their data sets.

\subsection[Normal-Normal]{Normal-Normal}
The following is a general Normal-Normal hierarchical model. For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates \emph{j}-th group in the data set.
\begin{equation}
y_{j}\vert \mu_{j} \stackrel{ind}{\sim}\textrm{Normal}(\mu_{j}, V_{j}),
\end{equation}
\begin{equation}
\mu_{j}\vert \beta, A\stackrel{ind}{\sim}\textrm{Normal}(\mu_{0j}, A),
\end{equation}

where $~j=1, \ldots k$, $\mu_{0j} = x^{T}_{j} \mathbf{\beta}$, $x_{j}$ is the $j$-th group's covariate vector ($m\times 1$), $m$ is the number of regression coefficients and $\mathbf{\beta}$ and $A$ are unknown. Note that if there is no covariate then $x_{j}=1$ for an intercept term ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution. For reference, a parameter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean. Based on this conjugate prior distribution it is easy to derive the corresponding posterior distribution
\begin{equation} \label{normalpost}
\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})V_{j}),
\end{equation}
where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, k$, are called shrinkages.

@@

where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$. Note that $r$ and $\beta$ are two unknown hyper-parameters. Then, corresponding posterior distribution is
\begin{equation} \label{betapost}
p_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+n_{j}y_{j},~r(1-p_{0j})+n_{j}(1-y_{j}))\sim\textrm{Beta}\bigg[p^{\ast}_{j},~ \frac{p^{\ast}_{j}(1-p^{\ast}_{j})}{r+n_{j}+1}\bigg],
\end{equation}
where $p^{\ast}_{j}\equiv(1-B_{j})y_{j}+B_{j}p_{0j}$, $B_{j}\equiv r/ (r+n_{j})$, and $y_{j}\equiv z_{j} / n_{j}$, $j=1,\ldots,k$.

@@

where $m$ is the number of regression coefficients. As for $\beta$, it is a reasonable choice to assume a flat (non-informative) distribution because information about the location gets plentiful as the number of groups increases. The next flat prior distribution of the second-level variance component $A$ (or $1/r$) was chosen for its good repeated sampling properties and for posterior propriety under moderate conditions.

@@

\subsection[Shrinkage Estimation]{Shrinkage Estimation}
Estimating the shrinkage factors ($B_1, \ldots B_k$) is the key estimation problem with the hierarchical models \code{gbp} assumes. As we can see in \ref{normalpost}, \ref{gammapost}, and \ref{betapost}, the posterior means are a linear function of the shrinkage factors and the posterior variances are also linear (Gaussian), quadratic (Poisson), or cubic (Binomial) functions. A natural method then to estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ is to first estimate the shrinkage factors.

\subsection[ADM]{Adjustment for Density Maximization}
It is noted that the shrinkage factors ($B_1, \ldots B_k$) are a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models. Current popular methods of estimation via maximization (MLE or MAP) of these unknown shrinkage factors can result in estimates lying on the boundary of the parameter space. In the Normal-Normal model this situation typically arises when the variation within schools is greater than the variation between resulting in a parameter estimate of $\hat{A} = 0$. %TODO: Reference this! Maybe it's in the Lysy paper

@@

Once we estimate these two moments of shrinkage, we can also estimate the posterior moments given only the data. Taking the Normal-Normal model as an example we note the following identities
\begin{eqnarray}
E(\mu_{j}\vert \textbf{y}) & = & E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y}) \\ 
Var(\mu_{j}\vert \textbf{y}) & = & E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y}).
\end{eqnarray}  
Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are functions of the shrinkage factors (\ref{normalpost}) and since we have already can estimate $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$ via ADM, we can finally estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$.

\subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Matching Moments}
After estimating the two posterior moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, \code{gbp} reasonably approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments. For the Binomial-Beta model we approximate $p_{j}\vert \textbf{z}$ with a Beta distribution and for the Poisson-Gamma model we approximate $\lambda_{j}\vert \textbf{z}$ with a Gamma distribution. Finally for the Normal-Normal model we actually estimate the first three moments and approximate $\mu_{j}\vert \textbf{y}$ with a skewed-t distribution. %TODO: should I put down the form of the skewed-t or just put a reference to it?

@@

There are two kinds of model justification processes; one is a model checking and the other is a method checking. The model checking is for the justification of the model \ref{multilevel} on a specific data set. One possible question is, ``Can this data set benefit from such a multilevel modeling?'' \cite{1997} answered this question by using the Negative-Binomial mixture model on Poisson data to justify the second-level hierarchy. They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.

Once we are sure that the hierarchical modeling can be appropriate for our data, the following question will be about the validity of interval estimates, the final product of this multilevel modeling. ``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to check this point. From now on, all the explanations will be based on the Binomial model using the baseball data because the idea is the same and can be easily applied to the other two models.

\subsection{Pseudo-data Generation Process}
Figure 1 will be helpful to understand this process. As we can see in (8), the distribution of each true batting average ($p_{j},~j=1,\ldots, 18$) depends on two hyper-parameters, $r$ and $\beta_{(2\times1)}$. So, once we fix these hyper-parameters at specific values, we can generate true batting averages. Suppose we sampled 500 $\mathbf{p}_{(18\times1)}$'s, \emph{i.e.}, $\{\mathbf{p}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (8), where $r$ and $\beta$ are given. Then, we can also generate $\{\mathbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates the $i$-th pseudo-data set and $j$ does the $j$-th player. Next, \code{coverage} fits the Binomial hierarchical model 500 times on $\{(\mathbf{z}^{(i)}_{(18\times1)}, \mathbf{n}_{(18 \times 1)}),~i=1, \ldots, 500\}$ to obtain 500$\times$18 interval estimates.  After this generating process, as for the first player, we will have 500 pairs of ($z_{i1}$, $p_{i1}$) and 500 interval estimates, $\{(\hat{p}_{i1, low}, ~\hat{p}_{i1, upp}$), $i=1, \ldots, 500\}$.
\begin{figure}[h]
\begin{center}
\includegraphics[width=5cm]{process.png}
\caption{Pseudo-data generating process}
\end{center}
\end{figure}

\subsection{Simple Unbiased Estimates of Coverage Probabilities}
Based on the generated pseudo-data sets, let's define an indicator variable, $I_{ij}$, which is 1 if the $j$-th player's interval estimate from the $i$-th pseudo-data set includes $p_{ij}$ and 0 otherwise. One way to estimate the coverage probability is taking average over these indicator variables. We call it a simple unbiased coverage probability estimate. For example, $\bar{I}_{1}=\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first player.

\subsection{Rao-Blackwellized Unbiased estimates of Coverage Probabilities}
Rao-Blackwellization improves accuracy of an unbiased estimator by taking conditional expectation given a sufficient statistic. Based on this idea, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were given at first (see 5.1) and $z_{ij}$ is a sufficient statistic. This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is the $j$-th player's interval estimates on the $i$-th data set. We can calculate this probability  because we know the distribution of $p_{ij} \vert z_{ij}, r, \beta$ in (9). Note that conditioning on $z_{ij}$ is equivalent to conditioning on $\mathbf{z}$ as long as $r$ and $\beta$ are known. Then, we can estimate the first player's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$, which is also unbiased but more accurate than the previous simple estimator.

%TODO: Proof read Hospital and Baseball examples
\section[Examples]{Examples}
\subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
Suppose you live in the New York state (NY) and have been suffering from severe coronary heart disease. If you are supposed to receive the coronary artery bypass graft (CABG) surgery soon, you might want to find the most famous hospital for dealing with such a surgery. On top of that, if you can figure out each hospital's ability to handle this surgery, it will be useful for your decision in choosing a hospital.

For this purpose, you gathered data of 31 hospitals in NY composed of the number of deaths within a month of CABG surgeries and total number of patients receiving CABG surgeries in each hospital. In addition, while one looks for such information, suppose one knows that the state-level death rate per exposure of this surgery is 0.020.

The multilevel modeling that assumes a bigger population-level hierarchy will be insightful in this problem. Here, we presume a state-level (NY) hierarchy governing the true death rates of CABG surgery of all the hospitals in NY. This perspective is to view the true death rates of those 31 hospitals as sampled from the state-level population distribution whose mean is 0.020. For reference, a model check can be useful for evaluating the validity of such a view point (Christiansen and Morris, 1996).

Assuming an additional hierarchy is reasonable, a model-fitting process begins.  Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$) in each hospital, the Poisson distribution would be the first choice to describe the uncertainty in our data. Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in 3.2 . For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression (see section 3.2).
\begin{CodeChunk}
\begin{CodeInput}
R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "pr")
R> p
\end{CodeInput}
\begin{CodeOutput}
Summary for each unit (sorted by n):

>>>>

%% an abstract and keywords
\Abstract{
\pkg{Rgbp} is an R package for estimating and validating a two-level model (a random-effects mixed model). The estimation procedure utilizes Bayesian machinery and the validation involves checking frequency properties of the procedure via repeated sampling (which we call ``method checking"). It is found that \pkg{Rgb} characterized by such Bayesian-frequentist reconciliation has strong points of both sides, working well in small samples and yielding good coverage probability. Following three examples for Gaussian, Poisson and Binomial data support this argument.}
\Keywords{hierarchical model, multilevel model, random effects mixed model, method checking, coverage probability, Normal, Poisson, Binomial,  shrinkage, \proglang{R}}
\Plainkeywords{keywords, comma-separated, not capitalized, r} %% without formatting
%% at least one keyword must be supplied

@@

%\section[Feasible Data Types]{Three Feasible Types of Data }
%\pkg{Rgbp} is intended to fit a model where two levels of structure are assumed (unit and group levels). The model can be characterized by the distributional family assumed for the group level data and in the case of \pkg{Rgbp} this will be either the Normal, Poisson, or Binomial distribution. In this section, we will introduce three specific types of feasible data sets that illustrate this fact.

%\subsection{Normal: 8 Schools} \label{8schooldata}
%The Education Testing Service (ETS) conducted randomized experiments in eight separate schools (group) to test whether students (unit) SAT scores are effected by coaching. The dataset contains the estimated coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of the eight schools \cite{1981}.
%\begin{CodeChunk}
%\begin{CodeInput}
%R> y  <- c(12, -3, 28,  7,  1,  8, 18, -1)
%R> se <- c(18, 16, 15, 11, 11, 10, 10,  9)
%\end{CodeInput}
%\end{CodeChunk}

%Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated. So, it is reasonable to think that each school-level coaching effect is distributed as an independent Normal distribution given the unknown mean $\mu_{j}$ and known standard error:  $y_{j}\vert\mu_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$. \pkg{Rgbp} includes this data set and can be called by the command `\code{data(schools)}' on \proglang{R}.

%\subsection{Poisson: 31 Hospitals}
%The following data are from medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 \cite{2012}. It comprises of the number of deaths within a month of CABG surgeries in each hospital ($z_{j},~j=1, \ldots, 31$) and the total number of patients receiving CABG surgeries (case load) in each hospital ($n_{j},~j=1, \ldots, 31$). The following code is an example of input based on the last ten hospital data.
%\begin{CodeChunk}
%\begin{CodeInput}
%R> z <- c( 14,   9,  15,  13,  35,  26,  25,  20,   35,   27)
%R> n <- c(593, 602, 629, 636, 729, 849, 914, 940, 1193, 1340)
%\end{CodeInput}
%\end{CodeChunk}
%Considering the type of data, it is reasonable to assume the number of deaths in each hospital follow independent Poisson distributions given an unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where, for each $j$, $n_{j}$ can be interpreted as an exposure (not necessarily an integer) and $\lambda_{j}$ as the true death rate per exposure. This data set is also included in the package and can be called by `\code{data(hospital)}' on \proglang{R}.

%\subsection{Binomial: 18 Baseball Hitters}
%The following dataset contains information on the batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season \cite{1975}. In addition one covariate relating to the position each player was playing was observed and for illustrative purposes, we transform this variable into a binary indicator (1 if a player was an outfielder and 0 otherwise).
%\begin{CodeChunk}
%\begin{CodeInput}
%R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  %8,  7)
%R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, %45, 45)
%R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
%\end{CodeInput}
%\end{CodeChunk}
%The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown true batting average $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$. This data set is also a part of the package and can be called on \proglang{R} by `\code{data(baseball)}'.

\section[Multilevel Structure]{Multilevel Structure} \label{multilevel}
A two-level or multilevel model, also called a conditionally independent hierarchical model \cite{1989}, is a very powerful tool for exploring the hierarchical structure in data. For example, we can imagine that there exists a district-level hierarchy (bigger population) for observed school-level data, or a state-level hierarchy for observed hospital data in a certain state.

\code{gbp}, one of the functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter. The \code{gbp} function allows users to choose one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their data sets.

\subsection[Normal-Normal]{Normal-Normal}
The following is a general Normal-Normal hierarchical model. For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates the \emph{j}-th group among \emph{k} groups in the data set.
\begin{equation}
y_{j}\vert \mu_{j} \stackrel{ind}{\sim}\textrm{Normal}(\mu_{j}, V_{j}),
\end{equation}
\begin{equation}
\mu_{j}\vert \beta, A\stackrel{ind}{\sim}\textrm{Normal}(\mu_{0j}, A),
\end{equation}

where $\mu_{0j} = x^{T}_{j} \mathbf{\beta}$, $j=1, \ldots k$, $x_{j}$ is the $j$-th group's covariate vector ($m\times 1$), $m$ is the number of regression coefficients and both $\mathbf{\beta}$ and $A$ are unknown. Note that if there is no covariate then $x_{j}=1$ for an intercept term ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution. For reference, a parameter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean. Based on this conjugate prior distribution it is easy to derive the corresponding posterior distribution
\begin{equation} \label{normalpost}
\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})V_{j}~),
\end{equation}
where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, k$, are called shrinkages.

@@

where $\log(\frac{p_{0j}}{1-p_{0j}}) =x_{j}'\beta, ~j=1, \ldots, k$ and $r$ and $\beta$ are two unknown hyper-parameters. Then, corresponding posterior distribution is
\begin{equation} \label{betapost}
p_{j}\vert \textbf{z}, \beta, r \stackrel{ind}{\sim}\textrm{Beta}(rp_{0j}+n_{j}y_{j},~r(1-p_{0j})+n_{j}(1-y_{j}))\sim\textrm{Beta}\bigg[p^{\ast}_{j},~ \frac{p^{\ast}_{j}(1-p^{\ast}_{j})}{r+n_{j}+1}\bigg],
\end{equation}
where $p^{\ast}_{j}\equiv(1-B_{j})y_{j}+B_{j}p_{0j}$, $B_{j}\equiv r/ (r+n_{j})$, and $y_{j}\equiv z_{j} / n_{j}$, $j=1,\ldots,k$.

@@

where $m$ is the number of regression coefficients. As for $\beta$, it is a reasonable choice to assume a flat (non-informative) distribution because information about the location gets plentiful as the number of groups (\emph{k}) increases. The next flat prior distribution of the second-level variance component $A$ (or $1/r$) was chosen for its good repeated sampling properties and for posterior propriety under moderate conditions.

@@

\subsection[Shrinkage Estimation]{Shrinkage Estimation}
Estimating the shrinkage factors ($B_1, \ldots B_k$) is the key estimation problem with the hierarchical models \code{gbp} assumes. As we can see in (\ref{normalpost}), (\ref{gammapost}), and (\ref{betapost}), the posterior means are a linear function of the shrinkage factors and the posterior variances are also linear (Gaussian), quadratic (Poisson), or cubic (Binomial) functions. A natural method then to estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$ is to first estimate the shrinkage factors.
%TODO: If we cite somgthing, (Morris, 2011) might be appropriate format to me, but in our case it looks Morris (2011), which is confusing.

\subsection[ADM]{Adjustment for Density Maximization}
It is noted that the shrinkage factors ($B_1, \ldots B_k$) are a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models. Current popular methods of estimation via maximization (MLE or MAP) of these unknown shrinkage factors can result in estimates lying on the boundary of the parameter space. In the Normal-Normal model \cite{2012} this situation typically arises when the within-group variation is greater than the between-group variation resulting in a parameter estimate of $\hat{A} = 0$.

@@

Once we estimate these two moments of shrinkage, we can also estimate the posterior moments given only the data ($\textbf{y}$). Taking the Normal-Normal model as an example we note the following identities
\begin{eqnarray}
E(\mu_{j}\vert \textbf{y}) & = & E(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}) =E((1-B_{j})y_{j}+B_{j}\mu_{0j}\vert \textbf{y}).\\ 
Var(\mu_{j}\vert \textbf{y}) & = & E(Var(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, \beta, A)\vert \textbf{y}).
\end{eqnarray}  
Note that both $E(\mu_{j}\vert \textbf{y}, \beta, A)$ and $Var(\mu_{j}\vert \textbf{y}, \beta, A)$ are linear functions of the shrinkage factors as specified in (\ref{normalpost}) and since we can estimate $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$ via ADM, we can finally estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$.

\subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Matching Moments}
After estimating the two posterior moments, for example $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$, \code{gbp} reasonably approximates a posterior distribution of the mean effects given the data by assuming a reasonable distribution and matching moments. For the Binomial-Beta model we approximate $p_{j}\vert \textbf{z}$ with a Beta distribution and for the Poisson-Gamma model we approximate $\lambda_{j}\vert \textbf{z}$ with a Gamma distribution. Finally for the Normal-Normal model we actually estimate the first three moments and approximate $\mu_{j}\vert \textbf{y}$ with a skewed-t distribution.

%TODO: should I put down the form of the skewed-t or just put a reference to it?

@@

% TODO: Here, Christiansen and Morris (1997) seems appropriate format
There are two kinds of model justification processes; one is a model checking and the other is a method checking. The model checking is for the justification of the model \ref{multilevel} on a specific data set. One possible question is, ``Can this data set benefit from such a multilevel modeling?'' \cite{1997} answered this question by using the Negative-Binomial mixture model on Poisson data to justify the second-level hierarchy. They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.

Once we are sure that the hierarchical modeling can be appropriate for our data, the following question will be about the validity of interval estimates, the final product of this multilevel modeling. ``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' \pkg{Rgbp} has a function called \code{coverage} to answer this question and it comprises of two parts, generating peudo-dataset and estimating coverage probability.

For reference, the explanation will be based on Normal-Normal model because the idea can be easily applied to other two models.

\subsection{Pseudo-data Generation Process}
Figure 1 will be helpful to understand this process. As we can see in (\ref{normalpost}), the distribution of each true parameter ($\mu_{j},~j=1,\ldots, k$) is completely determined by two hyper-parameters, $A$ and $\beta_{(m\times1)}$. So, once we fix these hyper-parameters at specific values, we can generate true parameters. Suppose we sampled 500 $\mathbf{\mu}_{(k\times1)}$'s, \emph{i.e.}, $\{\mathbf{\mu}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (2), where $A$ and $\beta$ are given. Then, we can also generate $\{\mathbf{y}^{(i)}_{(k\times1)},~i=1, \ldots, 500\}$ given each $\mu_{ij},$ where $i$ indicates the $i$-th pseudo-data set and $j$ does the $j$-th group.

\begin{figure}[h]
\begin{center}
\includegraphics[width=5cm]{process.png}
\caption{Pseudo-data generating process}
\end{center}
\end{figure}

\subsection{Coverage Estimation Process}
Next, \code{coverage} fits the Normal-Normal model 500 times using the 500 peudo-datasets in order to obtain 500$\times$k interval estimates.

\subsubsection{Simple Unbiased Estimates of Coverage Probabilities}
Let's define an indicator variable, $I_{ij}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu_{ij}$ and 0 otherwise. One way to estimate the coverage probability is taking average over these indicator variables. We call it a simple unbiased coverage probability estimate. For example, $\bar{I}_{1}=\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first group.

\subsubsection{Rao-Blackwellized Unbiased estimates of Coverage Probabilities}
Rao-Blackwellization improves accuracy of an unbiased estimator by taking conditional expectation given a sufficient statistic. Based on this idea, we define $E(I_{ij}\vert y_{ij}, A, \beta$), where $A$ and $\beta$ were given at first (see 4.1) and $y_{ij}$ is a sufficient statistic. This expectation is the same as Pr$(\hat{\mu}_{ij, low}\le \mu_{ij} \le\hat{\mu}_{ij, upp}\vert y_{ij}, A, \beta)$, where ($\hat{\mu}_{ij, low}$, $\hat{\mu}_{ij, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset. We can calculate this probability  because we know the distribution of $\mu_{ij} \vert y_{ij}, A, \beta$ in (\ref{normalpost}). Note that conditioning on $y_{ij}$ is equivalent to conditioning on $\mathbf{y}$ as long as $A$ and $\beta$ are known. Then, we can estimate the first group's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert y_{i1}, A, \beta)/500$, which is also unbiased but more accurate than the previous simple estimator.

\section[Examples]{Examples}
\subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
Suppose a person living in the New York state (NY) has been suffering from severe coronary heart disease. If this person is supposed to receive the coronary artery bypass graft (CABG) surgery soon, he or she might want to find the most reliable hospital for dealing with such a surgery. On top of that, if this person can figure out each hospital's ability to handle this surgery, it will be useful for choosing a hospital.

For this purpose, you gathered data of 31 hospitals in NY composed of the number of deaths ($z$) within a month of CABG surgeries and total number of patients ($n$) receiving CABG surgeries in each hospital. The following code is an example of input based on the last ten hospital data.
\begin{CodeChunk}
\begin{CodeInput}
R> z <- c( 14,   9,  15,  13,  35,  26,  25,  20,   35,   27)
R> n <- c(593, 602, 629, 636, 729, 849, 914, 940, 1193, 1340)
\end{CodeInput}
\end{CodeChunk}

In addition, while one looks for such information, suppose one knows that the state-level death rate per exposure of this surgery is 0.020.

The multilevel modeling that assumes a bigger population-level hierarchy will be insightful in this problem. Here, we presume a state-level (NY) hierarchy governing the true death rates ($\lambda$) of CABG surgery of all the hospitals in NY. This perspective is to view the true death rates of those 31 hospitals as sampled from the state-level population distribution whose mean is 0.020.

Assuming an additional hierarchy is reasonable, a model-fitting process begins.  Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$) in each hospital, the Poisson distribution would be the first choice to describe the uncertainty in our data. Note that caseload  ($n_{j}$) can be interpreted as an exposure, which is not necessarily an integer.

Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in 2.2 . For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression (see section 3.2).
\begin{CodeChunk}
\begin{CodeInput}
R> data(hospital)
R> z <- hospital$z
R> n <- hospital$n
R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "pr")
R> p
\end{CodeInput}
\begin{CodeOutput}
Summary for each unit (sorted by n):
